Behavior Driven Development in Haskell

### 2012-05-31 paper.tex
Describe solution for spec discovery

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\emph{optional} Automatic discovery of specs}
TBD

>>>>

\subsection{Automatic discovery of specs}
\label{sec:problem-discovery}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Automatic discovery of specs}
We want to automatically discover all specs of a project, so that we
can run them all together.  This requires to automatically generate
boilerplate code, similar to what is shown in
\ref{sec:problem-discovery}.

We make creative use GHC's mechanism for custom preprocessors for
that.  With our solution, the developer creates test driver, that only
contains a single line:

This tells GHC to run a preprocessor, \verb|hspec-discover| on the
source file.  \verb|hspec-discover| finds all specs for a project, and
generates a suitable test driver.

This approach relies on the following conventions
\begin{enumerate}
    \item
        Spec files have to be placed into the same directory as the
        test driver, or into a subdirectory.
    \item
        The name of a spec file has to end in \verb|Spec.hs|, and the
        module name has to match the file name.
    \item
        Each spec file has to provide a top-level binding \verb|spec|,
        of type \verb|Spec|.
\end{enumerate}

It would be possible to lift some of those requirements.  But we think
they are reasonable conventions, anyway.
